---
title: "Uploading a Course to the Socratic Swirl system"
author: "David Robinson and Dima Gorenshteyn"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Uploading a Course to the Socratic Swirl system}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r}
library(knitr)
opts_chunk$set(eval = FALSE)
```

You're welcome to give your students the exercises that we built in, but you probably want to offer your own in-class exercises. Here are simple instructions for uploading up your own quiz within SocraticSwirl, so that your students can take it.

First, make sure you've signed in with `socratic_swirl_login` (or created an instructor account with `socratic_swirl_signup` if you haven't already).

### Creating Exercises

Exercises are created in SocraticSwirl the same way they are created for Swirl. [Here](http://swirlstats.com/instructors.html) you can read in detail about creating interactive exercises using the "swirlify" tool. In short, quiz questions are structured as [YAML](http://en.wikipedia.org/wiki/YAML) files, in a form something like this:

    - Class: cmd_question
      Output: Now store the contents of the 'cars$mpgCity' in a new variable called 'myMPG'.
      CorrectAnswer: myMPG <- cars$mpgCity
      AnswerTests: newcmd=myMPG <- cars$mpgCity
      Hint: Use the assignment operator to assign 'cars$mpgCity' to a new variable called
        'myMPG'.

Alternatively you could write a multiple choice question:

    - Class: mult_question
      Output: Mean, median, and mode are all measures of ____________.
      AnswerChoices: variation; significance; deviation; central tendency
      CorrectAnswer: central tendency
      AnswerTests: word=central tendency
      Hint: This is a fancy term for the "middle" of a dataset.

**Note**: in regular Swirl, questions are usually interspersed with text paragraphs and demonstrations. This is probably not the right approach for a set of SocraticSwirl exercises, since your students will be taking them in your class. Instead, make each of your items a question (either multiple choice or command-based).

### Uploading your exercises

Now you've created one or more lessons in your course, which you put into a directory called `my_course`. Suppose it has one lesson in it, called `my_lesson`. Time to upload it!

```{r, eval = FALSE}
upload_course("my_course")
```

Your students can then install and take your lesson with the following line of code. *Make sure* they include the instructor username in the function, which allows you to view the results.

```{r, eval = FALSE}
socratic_swirl("my_lesson", "my_course", instructor = "your_username")
```

Then to view the results in real-time, simply run the dashboard and select that course:

```{r, eval = FALSE}
dashboard()
```
